Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-08 ms.tex
changing mn2e

\makeatletter
\newlength{\abovecaptionskip}%
\setlength{\abovecaptionskip}{10\p@}
\makeatother
\usepackage{threeparttable}

@@

%    Overall we conclude that for values of $\Mbh\lsim 10^{8} \Msun$,
 %   the observed nuclear x-ray luminosities in quiescent, early type
  %  galaxies could be understood as coming from thermally stable
   % steady-state accretion of stellar winds shed in the galactic
    %nucleus.

We conclude by drawing attention to the following limitations of our model
    \begin{enumerate}
    \item Overall the accretion rate onto the central SMBH will be strongly
    tied to the properties of the stellar population (e.g. age) within
    the sphere of influence of the black hole. Thus, our model cannot
    say anything definitive about the mode accretion for individual
    galaxies which may have significant variations about our assumed
    average SFHs.
    \item Also, the SFH of bulges may (and probably
      does) systematically differ from the average star formation
      history for galaxies as a whole.
    \item Furthermore, there could be a radial gradient in the star
      formation history within a given bulge... 
     {\bf AG this section needs to be finished...}
    \end{enumerate}

>>>>

\makeatletter
\newlength{\abovecaptionskip}%
\setlength{\abovecaptionskip}{10\p@}
\makeatother
%\renewcommand{\citeauthoryear}[3]{}

\usepackage{threeparttable}

@@

We conclude by drawing attention to the following limitations of our model
    \begin{enumerate}
    \item We assume that there is no large scale inflow of gas to the
      nucleus, and the only source of gas feeding the black hole is
      stellar wind mass loss from the local stellar population. Thus,
      our estimates of gas density are a lower bound on the nuclear
      gas density {\bf AG: make sense?}.

      As we have already pointed out AGN activity cannot be explained
      by steady thermally stable accretion of mass lost from stellar
      winds.

    \item Overall the accretion rate onto the central SMBH will be
      strongly tied to the properties of the stellar population
      (e.g. age) within the sphere of influence of the black
      hole. Thus, our model cannot say anything definitive about the
      mode accretion for individual galaxies unless something is known
      about their specific star formation history.

    \item We adopt halo average star formation rates measured in
      cosmological simulations by \citet{MosterNaab+:2013a}, and
      neglect any spatial variation in the star formation rate for any
      given galaxy. Galaxies with masses$\gsim 7\times 10^{10} \Msun$,
      assemble their stars from the inside out
      \citet{PerezCidFernandes+:2013a}
      and so for a given halo mass
      the galactic nucleus may be significantly older than in our
      model and thus more prone to thermal instability.

      On the other hand, \citealt{LauerFaber+:2005a} find that $\sim
      60\%$ of cusp galaxies and $\sim29\%$ of core galaxies have
      (generally unresolved) emission in excess of the inward
      extrapolation of the Nuker law, and noted that these nuclei are bluer
      than the background galaxy starlight, suggesting the presence of
      younger stars towards the center of the galaxy.

      In fact it is possible that the mass injection is in fact
      dominated by a nuclear star cluster with a break radius on
      parsec scales. Although this is much smaller than our fiducial
      break radius (100 pc). If the heating is sufficiently high
      moving the break radius inwards would merely change the outer
      gas density profile, without changing the stagnation radius in
      the flow and thus the accretion rate onto the black hole. Of
      course if one moves the break radius to where the stagnation
      radius would be the stagnation radius would move inwards
      somewhat. However note the for high heating rate ($v_w \gsim 500
      $ km/s and small black hole masses $\Mbh \lsim 10^7 \Msun$), we
      predict stagnation radii smaller than a parsec.
